---
title: 'Developing Data Products - Most Harmful US Storm Events'
author: "Christine Grayson"
output:
  html_document:
    df_print: paged
    self_contained: yes
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressWarnings(suppressMessages(library(knitr)))
suppressWarnings(suppressMessages(library(dplyr)))
suppressWarnings(suppressMessages(library(ggplot2)))
suppressWarnings(suppressMessages(library(tidyr)))
suppressWarnings(suppressMessages(library(readr)))
suppressWarnings(suppressMessages(library(kableExtra)))
suppressWarnings(suppressMessages(library(plotly)))
```
#### 10/22/2021

## Synopsis

This project is created for week three of the peer graded assignment of the course "Developeing Data Products" offered by Johns Hopkins University through Coursera.

The aim is to produce a plotly graph. I thought I would repeat one of the graphs (produced in ggplot) from my submission for the course "Reproducible Research" which can be found [here](https://rpubs.com/graysonch/750089). The bar chart shows the most severe storms to personal safety. 

```{r, echo = FALSE}

zipped_file <- "StormData.csv.bz2"
if(!file.exists(zipped_file)){
    dest_file_path <- file.path("./")
    fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
    download.file(fileUrl,destfile=zipped_file,method="curl")
}
```

```{r, echo = FALSE, cache = TRUE}
if(file.exists(zipped_file)) {
    stormData <- read.csv(file=zipped_file)
    
} else {
    knit_exit()("No data, exiting!")
}
```

```{r, echo = FALSE}
positive_harm_table <- stormData[!(stormData$FATALITIES == 0 & stormData$INJURIES == 0 & stormData$PROPDMG == 0 & stormData$CROPDMG == 0),]
unique_envtypes <- unique(sort(positive_harm_table$EVTYPE))
#print(length(unique_envtypes))

# cols <- 50
# suppressWarnings(length(unique_envtypes) <- prod(dim(matrix(unique_envtypes, ncol=cols))))
# as.data.frame(t(matrix(unique_envtypes, ncol=cols)))

```

```{r, echo = FALSE}
positive_harm_table$EVTYPE<-gsub(" ", "_", positive_harm_table$EVTYPE)
positive_harm_table$EVTYPE<-gsub("/", "_", positive_harm_table$EVTYPE)
positive_harm_table$EVTYPE<-gsub("__", "_", positive_harm_table$EVTYPE)
positive_harm_table$EVTYPE <- toupper(positive_harm_table$EVTYPE)

# Avalanche
positive_harm_table$EVTYPE<-gsub("AVALANCE", "AVALANCHE", positive_harm_table$EVTYPE)

# Blizzard
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("BLIZZARD",EVTYPE), "BLIZZARD", EVTYPE))

# Coastal Flood
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^COASTAL_FLOOD",EVTYPE) |
                         grepl("^COASTAL_EROSION",EVTYPE) |
                         grepl("^COASTAL_SURGE",EVTYPE) |
                         grepl("^EROSION_CSTL_FLOOD",EVTYPE) |
                         grepl("^TIDAL_FLOODING",EVTYPE), "COASTAL_FLOOD", EVTYPE))

# Cold / Windchill
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^COLD",EVTYPE) |
                         grepl("^COOL_AND_WET",EVTYPE) |
                         grepl("^LOW_TEMPERATURE",EVTYPE) |
                         grepl("^UNSEASONABLY_COLD",EVTYPE) |
                         grepl("^EXTENDED_COLD",EVTYPE) |
                         grepl("^UNSEASONABLE_COLD",EVTYPE) |
                         grepl("^HYPOTHERMIA",EVTYPE) |
                         grepl("^HYPERTHERMIA",EVTYPE), "COLD/WIND_CHILL", EVTYPE))

# Debris Flow
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("LANDSLIDES",EVTYPE) |
                         grepl("LANDSLIDE",EVTYPE) |
                         grepl("LANDSLUMP",EVTYPE) |
                         grepl("DEBRIS_FLOW",EVTYPE)  |
                         grepl("ROCK_SLIDE",EVTYPE), "DEBRIS_FLOW", EVTYPE))

# Drought
positive_harm_table$EVTYPE<-gsub("DROUGHT_EXCESSIVE_HEAT", "DROUGHT", positive_harm_table$EVTYPE)
positive_harm_table$EVTYPE<-gsub("HEAT_AND_DRY", "DROUGHT", positive_harm_table$EVTYPE)

# Dust Devil
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^DUST_STORM",EVTYPE), "DUST_STORM", EVTYPE))

# Dust Storm
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^DUST_DEVIL",EVTYPE) |
                         grepl("^BLOWING_DUST",EVTYPE) |
                         grepl("^LANDSPOUT",EVTYPE), "DUST_DEVIL", EVTYPE))

# Extreme Cold / Windchill
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^RECORD_COLD",EVTYPE) |
                         grepl("^EXTREME_WINDCHILL",EVTYPE) |
                         grepl("^EXTREME_WIND_CHILL",EVTYPE) |
                         grepl("^EXTREME_COLD",EVTYPE), "EXTREME_COLD/WIND_CHILL", EVTYPE))

# Flash Flood
positive_harm_table <- positive_harm_table %>%
     mutate(EVTYPE=ifelse(grepl("FLASH",EVTYPE) & grepl("FLOOD",EVTYPE), "FLASH_FLOOD", EVTYPE))
positive_harm_table <- positive_harm_table %>%
   mutate(EVTYPE=ifelse(grepl("^MUD",EVTYPE), "FLASH_FLOOD", EVTYPE))

# Flood
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^RIVER_FLOOD",EVTYPE) |
                         grepl("^SMALL_STREAM_FLOOD",EVTYPE) |
                         grepl("^ICE_JAM",EVTYPE) | # anything that begins ICE_JAM
                         grepl("^ICE_FLOWS$",EVTYPE) |
                         grepl("^ICE_FLOES$",EVTYPE) |
                         grepl("^MAJOR_FLOOD",EVTYPE) |
                         grepl("^MINOR_FLOODING",EVTYPE) |
                         grepl("^FLOOD_HEAVY_RAIN",EVTYPE) |
                         grepl("^HIGH_WATER",EVTYPE) |
                         grepl("^RURAL_FLOOD",EVTYPE) |
                         grepl("^URBAN",EVTYPE) |
                         grepl("^FLOODING",EVTYPE) |
                         grepl("^FLOODS",EVTYPE) |
                         grepl("^DAM_BREAK",EVTYPE) |
                         grepl("^FLOOD_RIVER_FLOOD",EVTYPE) |
                         grepl("^FLOOD_&_HEAVY_RAIN",EVTYPE) |
                         grepl("^BREAKUP_FLOODING",EVTYPE) |
                         grepl("^FLOOD_HEAVY_RAINS",EVTYPE) |
                         grepl("^RIVER_AND_STREAM_FLOOD",EVTYPE) |
                         grepl("^FLOOD_RAIN_WINDS",EVTYPE) |
                         grepl("^SNOWMELT_FLOODING",EVTYPE) |
                         grepl("^STREAM_FLOOD",EVTYPE), "FLOOD", EVTYPE))

# Frost/Freeze
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^FREEZ",EVTYPE) |
                         grepl("^HARD_FREEZE",EVTYPE) |
                         grepl("^DAMAGING_FREEZE",EVTYPE) |
                         grepl("^BLACK_ICE",EVTYPE) |
                         grepl("^ICE_ON_ROAD$",EVTYPE) |
                         grepl("^ICE_ROADS$",EVTYPE) |
                         grepl("^ICY_ROADS$",EVTYPE) |
                         grepl("^FROST",EVTYPE), "FROST/FREEZE", EVTYPE))

# Freezing Fog
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^GLAZE$",EVTYPE) |
                         grepl("FOG_AND_COLD_TEMPERATURES",EVTYPE), "FREEZING_FOG", EVTYPE))

# Dense Fog
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^FOG$",EVTYPE), "DENSE_FOG", EVTYPE))

# Hail
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HAIL",EVTYPE) | grepl("^SMALL_HAIL",EVTYPE), "HAIL", EVTYPE))

# Heavy Rain
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HEAVY_RAIN",EVTYPE) |
                         grepl("^RAIN",EVTYPE) |
                         grepl("^DROWNING",EVTYPE) |
                         grepl("^RAINSTORM",EVTYPE) |
                         grepl("^HEAVY_SHOWER",EVTYPE) |
                         grepl("^RECORD_RAINFALL",EVTYPE) |
                         grepl("^HVY_RAIN",EVTYPE) |
                         grepl("^RAIN_WIND",EVTYPE) |
                         grepl("^TORRENTIAL_RAINFALL",EVTYPE) |
                         grepl("^HEAVY_PRECIPITATION",EVTYPE) |
                         grepl("^EXCESSIVE_WETNESS",EVTYPE) |
                         grepl("^UNSEASONAL_RAIN",EVTYPE) |
                         grepl("^EXCESSIVE_RAINFALL",EVTYPE), "HEAVY_RAIN", EVTYPE))

# Heavy Snow
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HEAVY_SNOW",EVTYPE) | # anything that starts with heavy or excessive snow
                         grepl("^SNOW_HEAVY",EVTYPE) | # anything that starts with snow heavy
                         grepl("^SNOW_AND_HEAVY_SNOW",EVTYPE) |
                         grepl("^RECORD_SNOW",EVTYPE) |
                         grepl("^EXCESSIVE_SNOW",EVTYPE) , "HEAVY_SNOW", EVTYPE))

# Heat
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^UNSEASONABLY_WARM",EVTYPE) |
                         grepl("^WARM_WEATHER",EVTYPE) , "HEAT", EVTYPE))

# Excessive Heat
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^EXTREME_HEAT",EVTYPE) |
                         grepl("^RECORD_HEAT",EVTYPE) |
                         grepl("^RECORD_EXCESSIVE_HEAT",EVTYPE) |
                         grepl("^HEAT_WAVE",EVTYPE), "EXCESSIVE_HEAT", EVTYPE))

# High Surf
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HIGH_SURF",EVTYPE) |
                         grepl("__HIGH_SURF_ADVISORY",EVTYPE) |
                         grepl("^ASTRONOMICAL_HIGH_TIDE",EVTYPE) |
                         grepl("^BEACH_EROSION",EVTYPE) |
                         grepl("^HEAVY_SURF_HIGH_SURF",EVTYPE) |
                         grepl("^HIGH_TIDES",EVTYPE) |
                         grepl("^HEAVY_SURF",EVTYPE) |
                         grepl("^ROUGH_SURF",EVTYPE) |
                         grepl("^HIGH_SURF_AND_WIND",EVTYPE) |
                         grepl("^HAZARDOUS_SURF",EVTYPE) |
                         grepl("^HIGH_SWELLS",EVTYPE) |
                         grepl("^HEAVY_SWELLS",EVTYPE) |
                         grepl("^HIGH_SEAS",EVTYPE) |
                         grepl("^HEAVY_SEAS",EVTYPE) |
                         grepl("^ROUGH_SEAS",EVTYPE) |
                         grepl("^ROGUE_WAVE",EVTYPE) |
                         grepl("^HIGH_WAVES",EVTYPE), "HIGH_SURF", EVTYPE))

# High Wind
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HIGH_WIND",EVTYPE) |
                         grepl("^GUSTY_WIND",EVTYPE) |
                         grepl("^NON_TSTM_WIND",EVTYPE) |
                         grepl("^NON-SEVERE_WIND_DAMAGE",EVTYPE) |
                         grepl("^WIND",EVTYPE) |
                         grepl("^GRADIENT_WIND",EVTYPE) |
                         grepl("^HIGH_WIND_",EVTYPE), "HIGH_WIND", EVTYPE))

# High Wind - this needs to come after the reclassification of HIGH_WIND AND HIGH_SURGE above
# make sure we dont include anyting with an underscore after it.
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HIGH$",EVTYPE), "HIGH_WIND", EVTYPE))


# Hurricane (Typhoon)
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HURRICANE",EVTYPE)|
                         grepl("^TYPHOON",EVTYPE), "HURRICANE_TYPHOON", EVTYPE))

# Ice Storm and Ice (Ice is not a valid category)
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^ICE_STORM$",EVTYPE) |
                         grepl("^ICE_STRONG_WINDS$",EVTYPE) |
                         grepl("^SNOW_AND_ICE_STORM$",EVTYPE) |
                         grepl("^SNOW_ICE_STORM$",EVTYPE) |
                         grepl("^GLAZE_ICE_STORM$",EVTYPE), "ICE_STORM", EVTYPE))

# Lake-effect Snow
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^HEAVY_LAKE_SNOW",EVTYPE) |
                         grepl("^LAKE_EFFECT_SNOW",EVTYPE) |
                         grepl("^LAKE_SEASON_SNOW",EVTYPE), "LAKE-EFFECT_SNOW", EVTYPE))

# Lakeshore Flood
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^LAKE_FLOOD",EVTYPE) |
                         grepl("^LAKESHORE_FLOOD",EVTYPE), "LAKESHORE_FLOOD", EVTYPE))

# Lightning
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^LIGHTNING",EVTYPE) | # anything that starts with lightning
                         grepl("^LIGHTING$",EVTYPE) |
                         grepl("^LIGNTNING$",EVTYPE), "LIGHTNING", EVTYPE))

# OTHER - these are categories that don't really fit the storm data or are present in the official table
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^OTHER_",EVTYPE) |
                         grepl("^SEVERE_TURBULENCE$",EVTYPE) |
                         grepl("^APACHE_COUNTY$",EVTYPE) |
                         grepl("^\\?$",EVTYPE) |
                         grepl("^MARINE_MISHAP$",EVTYPE) |
                         grepl("^MARINE_ACCIDENT$",EVTYPE), "OTHER", EVTYPE))

# Rip Current
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^RIP_CURRENT",EVTYPE), "RIP_CURRENT", EVTYPE))
# anything that starts with rip_current

# Storm Surge Tide
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^STORM_SURGE",EVTYPE) |
                         grepl("^RAPIDLY_RISING_WATER$",EVTYPE), "STORM_SURGE/TIDE", EVTYPE))

# Sleet
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^SLEET",EVTYPE) | # anything that begins with sleet
                         grepl("^FALLING_SNOW_ICE$",EVTYPE) |
                         grepl("^SNOW_FREEZING_RAIN$",EVTYPE) |
                         grepl("^SNOW_SLEET$",EVTYPE) |
                         grepl("^SNOW_SLEET_FREEZING_RAIN$",EVTYPE) |
                         grepl("^LIGHT_FREEZING_RAIN$",EVTYPE),"SLEET", EVTYPE))

# Strong Winds
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^STRONG_WINDS$",EVTYPE) |
                         grepl("^SEVERE_WIND_DAMAGE",EVTYPE) |
                         grepl("^STORM_FORCE_WINDS$",EVTYPE),"STRONG_WIND", EVTYPE))

# Thunderstorm Wind (Correct all the various misspellings)
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("TSTM",EVTYPE) |
                         grepl("THUNDERSTROM",EVTYPE) |
                         grepl("TUNDERSTORMM",EVTYPE) |
                         grepl("TUNDERSTORM",EVTYPE) |
                         grepl("THUDERSTORM",EVTYPE) |
                         grepl("THUNDERTORM",EVTYPE) |
                         grepl("THUNERSTORM",EVTYPE) |
                         grepl("THUNDEERSTORM",EVTYPE) |
                         grepl("THUNDERESTORM",EVTYPE), "THUNDERSTORM", EVTYPE))

positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^THUNDERSTORM",EVTYPE) &
                        !grepl("^MARINE_THUNDERSTORM",EVTYPE), "THUNDERSTORM_WIND", EVTYPE))

positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^DRY_MI$",EVTYPE) |
                         grepl("^WHIRLWIND$",EVTYPE) |
                         grepl("^GUSTNADO$",EVTYPE) |
                         grepl("^SEVERE_THUNDERSTORM",EVTYPE) | #anything that starts with this
                         grepl("^DOWNBURST$",EVTYPE) |
                         grepl("MICROBURST",EVTYPE) |
                         grepl("MIRCOBURST",EVTYPE), "THUNDERSTORM_WIND", EVTYPE))
                         # anything with microburst in it

# Tornado
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^TORNADO",EVTYPE) | grepl("^TORNDAO",EVTYPE), "TORNADO", EVTYPE))

# Tropical Storm
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^TROPICAL_STORM",EVTYPE) | # anything starting with TROPICAL_STORM
                         grepl("^COASTALSTORM$",EVTYPE) |
                         grepl("^COASTAL_STORM$",EVTYPE), "TROPICAL_STORM", EVTYPE))

# Waterspout
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^WATERSPOUT",EVTYPE), "WATERSPOUT", EVTYPE))
# anything starting with waterspout

# Wildfire
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("FOREST_FIRE",EVTYPE) | # anything with FOREST_FIRE
                         grepl("^WILDFIRES$",EVTYPE) |
                         grepl("^BRUSH_FIRE$",EVTYPE) |
                         grepl("^GRASS_FIRES$",EVTYPE) |
                         grepl("^WILD_FIRES$",EVTYPE), "WILDFIRE", EVTYPE))

# Winter Storm
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("WINTER_STORMS",EVTYPE) |
                         grepl("WINTER_STORM_HIGH_WINDS",EVTYPE), "WINTER_STORM", EVTYPE))

# Winter Weather
positive_harm_table <- positive_harm_table %>%
    mutate(EVTYPE=ifelse(grepl("^WINTER_WEATHER",EVTYPE) | # anything that starts with this
                         grepl("^WINTRY_MIX$",EVTYPE) |
                         grepl("^GLAZE_ICE$",EVTYPE) |
                         grepl("^ICE$",EVTYPE) |
                         grepl("^ICE_AND_SNOW$",EVTYPE) |
                         grepl("^BLOWING_SNOW$",EVTYPE) |
                         grepl("^BLACK_WINTER_WEATHER$",EVTYPE) |
                         grepl("^THUNDERWINTER_WEATHER$",EVTYPE) |
                         grepl("^MIXED_PRECIP$",EVTYPE) |
                         grepl("^MIXED_PRECIPITATION$",EVTYPE) |
                         grepl("^EARLY_FROST$",EVTYPE) |
                         grepl("^SNOW",EVTYPE) | # anything left that begins with snow
                         grepl("^LIGHT_SNOWFALL$",EVTYPE) |
                         grepl("^LATE_SEASON_SNOW$",EVTYPE) |
                         grepl("^RAIN_SNOW$",EVTYPE) |
                         grepl("^THUNDERSNOW$",EVTYPE) |
                         grepl("^LIGHT_SNOW$",EVTYPE) |
                         grepl("^AGRICULTURAL_FREEZE$",EVTYPE) |
                         grepl("^HEAVY_MIX$",EVTYPE) |
                         grepl("SNOW_SQUALL$",EVTYPE), "WINTER_WEATHER", EVTYPE))

ph_unique_envtypes <- unique(sort(positive_harm_table$EVTYPE))
#print(length(ph_unique_envtypes))
suppressWarnings(length(ph_unique_envtypes) <- prod(dim(matrix(ph_unique_envtypes, ncol = 4))))

# matrix(ph_unique_envtypes, ncol=4) %>%
#     kbl(col.names = c(1:4),caption="Consolidated/Fixed EVTYPEs That Cause Harm") %>%
#     kable_styling(bootstrap_options = "striped", font_size = 10)

# positive_harm_table
# dim(positive_harm_table)

```   
    
```{r, echo=FALSE, comment=FALSE, warning=FALSE, message=FALSE, error=FALSE}

person_harm_table <- positive_harm_table[!(positive_harm_table$FATALITIES == 0 & positive_harm_table$INJURIES == 0),]

person_harm_table <- person_harm_table %>%
        group_by(EVTYPE) %>%
        summarize(INJURIES = sum(INJURIES,na.rm=TRUE),FATALITIES = sum(FATALITIES,na.rm=TRUE))

pivot_personal_harm <- person_harm_table %>%
    pivot_longer(!EVTYPE, names_to = "Harm", values_to = "Count")

#pivot_personal_harm
```

## Results

The following is a bar chart using a log scale for the y axis, this is to stop the top value from swamping everything else. In addition it has log color coding to make the extreme cases more visible. The bars are ordered by overall damage.  

```{r Figure1p, echo = FALSE, fig.height=12, fig.width=16, warning=FALSE}

injuries <- person_harm_table %>% plot_ly(x=~reorder(EVTYPE, -INJURIES),
                y = ~log10(INJURIES),
                name = "INJURIES",
                type = "bar",
                marker = list(color = ~log10(INJURIES), coloraxis="coloraxis"),
                width = 900, height = 800) %>%
                layout(xaxis = list(title = "Event Types",
                                   zeroline = FALSE),
                      yaxis = list(title = "INJURIES (LOG COUNT)",
                                   type = 'log10',
                                   zeroline = FALSE))

fatalities <- person_harm_table %>% plot_ly(x=~reorder(EVTYPE, -FATALITIES),
                y = ~log10(FATALITIES),
                name = "FATALITIES",
                type = "bar",
                marker = list(color = ~log10(FATALITIES), coloraxis="coloraxis"),
                width = 900, height = 800) %>%
                layout(xaxis = list(title = "Event Types", 
                                    zeroline = FALSE),
                      yaxis = list(title = "FATALITIES (LOG COUNT)",
                                   type = 'log10',
                                   zeroline = FALSE),
                      coloraxis=list(colorscale='RdBu'))
 
subp <- subplot(fatalities, injuries, nrows =2, titleY = TRUE, titleX = TRUE, shareY = TRUE, shareX = TRUE) %>%
    layout(title = "Count of Fatalities and Injuries for Harmful Storm Events", 
           coloraxis=list(colorscale='RdBu'), 
           showlegend = FALSE, 
           plot_bgcolor='#D3D3D3',
           font = list(family = 'Arial',
                       size = 10,
                       color = '#000000'),
           xaxis = list( 
               zerolinecolor = '#ffff', 
               zerolinewidth = 2,
               tickangle=270,
               gridcolor = 'ffff'), 
           yaxis = list( 
               zerolinecolor = '#ffff', 
               zerolinewidth = 2, 
               gridcolor = 'ffff'))

subp

```



  
  
  